The Impact of Tax Policy Evolution on Economic Development and Income Inequality

### 2024-02-20 paper/paper.qmd
Cite packages in the paper

This paper reproduces, replicates, and expands on these findings, using the R programming language [@citeR] and the 'tidyverse' [@citeTidyverse] packages. Within the 'tidyverse' package [@citeTidyverse], we used 'readr' [@citeReadr], 'dplyr' [@citeDplyr], 'tidyr' [@citeTidyr], and 'ggplot2' [@citeGgplot2]. It examines the implications of tax policy evolution on economic development and income inequality, which raises the research question: "How does the transition from indirect to direct taxation, alongside the dynamics of the informal sector, influence tax equity and economic development in low- and middle-income countries, and what are the implications for designing effective and equitable tax policies?"

@@

This paper used the R programming language [@citeR] and the 'tidyverse' [@citeTidyverse] packages for replication, reproduction, data cleaning, and analysis. Within the 'tidyverse' package [@citeTidyverse], we used 'readr' [@citeReadr], 'dplyr' [@citeDplyr], 'tidyr' [@citeTidyr], and 'ggplot2' [@citeGgplot2] for reading CSV files, manipulating data, tidying data, and creating graphs.

Data collection methods exhibit significant diversity among open sources. We conducted a data-cleaning procedure for reproduction, focusing on variable selection, simplifying variable names, and removing missing values. The variables selected from the original paper were chosen based on their relevance to our research question, relating to how does the transition from indirect to direct taxation, alongside the dynamics of the informal sector, influence tax equity and economic development in low- and middle-income countries, and what are the implications for designing effective and equitable tax policies?

@@

# Results

@@

# Discussion

>>>>

This paper reproduces, replicates, and expands on these findings, using the R programming language [@citeR], the 'tidyverse' [@citeTidyverse] 'labelled' [@citelabelled], 'patchwork' [@citepatchwork], and 'haven' [@citehaven] packages. Within the 'tidyverse' package [@citeTidyverse], we used 'readr' [@citeReadr], 'dplyr' [@citeDplyr], 'tidyr' [@citeTidyr], and 'ggplot2' [@citeGgplot2]. It examines the implications of tax policy evolution on economic development and income inequality, which raises the research question: "How does the transition from indirect to direct taxation, alongside the dynamics of the informal sector, influence tax equity and economic development in low- and middle-income countries, and what are the implications for designing effective and equitable tax policies?"

@@

This paper used the R programming language [@citeR] along with the 'tidyverse' package [@citeTidyverse], as well as the 'labelled' [@citelabelled], 'patchwork' [@citepatchwork], and 'haven' [@citehaven] packages for replication, data cleaning, and analysis. Within the 'tidyverse' package [@citeTidyverse], we used 'readr' [@citeReadr], 'dplyr' [@citeDplyr], 'tidyr' [@citeTidyr], and 'ggplot2' [@citeGgplot2] for reading CSV files, manipulating data, tidying data, and creating graphs.

Data collection methods exhibit significant diversity among open sources. We conducted a data-cleaning procedure for reproduction, focusing on variable selection, simplifying variable names, and removing missing values. The variables selected from the original paper were chosen based on their relevance to our research question, relating to how does the transition from indirect to direct taxation, alongside the dynamics of the informal sector, influence tax equity and economic development in low- and middle-income countries, and what are the implications for designing effective and equitable tax policies? Throughout the process, careful attention was paid to the measurement of variables to ensure the validity and reliability of this paper’s findings. Measurement considerations included defining operational definitions for key concepts and ensuring consistency in the measurement process across different variables. The robustness check conducted by analyzing data from various years shows the data remains consistent over time.

@@

# Results {#sec-results}

@@

# Discussion {#sec-discussion}
